Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-06-26 _tex/manuscript.tex
Built site for gh-pages

\includegraphics{figures/fig-data-strat.png}

@@

\includegraphics[width=0.4\textwidth,height=\textheight]{static/small-graph.png}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{figures/fig-model-midext-evo.png}

@@

\includegraphics{figures/fig-model-state-dist.png}

@@

\includegraphics{figures/fig-model-burnin-history.png}

@@

\includegraphics{figures/fig-model-prevalences-overall.png}

@@

\includegraphics{figures/fig-model-prevalences-with-ipsi.png}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{figures/fig-model-prevalences-midext.png}

@@

\includegraphics{figures/fig-model-risks.png}

@@

\caption{\label{fig-model-risks}Histograms over the predicted risk of
occult contralateral LNL II (left), III (middle), and IV (right)
invovlement, shown for some combinations of T-category, tumor
lateralization, and ipsilateral clinical involvement. Unless otherwise
mentioned in the legend, the entire contralateral side was assumed to be
clinically node negative.}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{figures/fig-model-marginal-pdf.png}

>>>>

\includegraphics{manuscript_files/mediabag/figures/fig-data-strat.pdf}

@@

\includegraphics[width=0.4\textwidth,height=\textheight]{manuscript_files/mediabag/static/small-graph.pdf}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{manuscript_files/mediabag/figures/fig-model-midext-evo.pdf}

@@

\includegraphics{manuscript_files/mediabag/figures/fig-model-state-dist.pdf}

@@

\includegraphics{manuscript_files/mediabag/figures/fig-model-burnin-history.pdf}

@@

\includegraphics{manuscript_files/mediabag/figures/fig-model-prevalences-overall.pdf}

@@

\includegraphics{manuscript_files/mediabag/figures/fig-model-prevalences-with-ipsi.pdf}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{manuscript_files/mediabag/figures/fig-model-prevalences-midext.pdf}

@@

\includegraphics{manuscript_files/mediabag/figures/fig-model-risks.pdf}

@@

\caption{\label{fig-model-risks}Histograms over the predicted risk of
occult contralateral LNL II (left), III (middle), and IV (right)
invovlement, shown for some combinations of T-category, tumor
lateralization, and clinical LNL diagnoses. All LNLs not explicitly
mentioned in the legend, including the LNL for which the risk of occult
disease was computed, where assumed to be clinically negative.}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{manuscript_files/mediabag/figures/fig-model-marginal-pdf.pdf}
